Universal Anonymous Signatures

### 2022-07-28 prism-backend/research/gsac/relationships.tex
Migrated syntax, model and construction where issuers=users. RS construction fixed.

  \scalebox{0.9}{
    \begin{minipage}[t]{\textwidth}
      \textbf{Issuance functions:}
      \begin{align}
        & \fissue^1(\cdot,\cdot,\cdot) \coloneqq 1 \nonumber \\
        & \fissue^{single,L}(\upk,\cdot,\cdot) \coloneqq
          \pcreturn \upk \notin L
          \nonumber \\
        & \fissue^{\sring}(\upk,\attrs,\cdot) \coloneqq
          \pcreturn (\attrs = \sring \land \upk \in \attrs) \nonumber \\
        & \fissue^{l,\dattrs}(\cdot,\attrs,(\cid,\cattrs)) \coloneqq
          \pcreturn (\attrs_1 = l+1 \land \attrs \subseteq
          \cup_{i\in\dattrs} \cattrs_i) \nonumber
      \end{align}

@@

\subsubsection{\CUASGS construction.} %
We show that the $(\fissue^{single,L},\feval^0,\finsp^{\upk})$-\CUASGen
restriction, is a secure group signature scheme according to \cite{bsz05}.
Observe that the $\fissue^{single,L}$ function is further parameterized with
a list $L$ maintained by the issuer and must be fetched by users prior to
joining. It restricts that any user can have at most one credential (associated
to a same user key pair). We first quickly define the algorithms, and then
prove security.

\begin{description}
\item[$(\gpk,\isk,\osk) \gets KeyGen(1^\secpar)$.] Runs the \Setup algorithm
  of \CUASGen, and one instance of \IKeyGen and \OKeyGen. Assigns the public
  keys to \gpk.
\item[$(\upk,\usk) \gets \UKeyGen(1^\secpar)$.] Runs \UKeyGen from \CUASGen.
\item[$\langle \cred,\utrans \rangle \gets
  \langle\Obtain(\usk,\ipk),\Issue(\isk,\upk)\rangle$.] Runs $\langle\Obtain,
  \Issue\rangle$ as in \CUASGen, with $\attrs \gets \emptyset$.
\item[$\sig \gets \Sign(\gpk,\cred,\msg)$.] Parses \gpk as $(\ipk,\opk)$, and
  runs $(\sig,0) \gets \Sign(\usk,\opk,\cred,\msg,\feval^0)$ from \CUASGen --
  note that $0$ is the constant output of $\feval^0$.
\item[$1/0 \gets \Verify(\gpk,\sig,\msg)$.] Parses \gpk as $(\ipk,\opk)$, and
  returns whatever $\Verify(\opk,\ipk,\sig,0,\msg,\feval^0)$ from \CUASGen
  outputs.
\item[$(\upk,\pi) \gets \Open(\gpk,\osk,\trans,\sig,\msg)$.] Parses \gpk as
  $(\ipk,\opk)$, and returns whatever \CUASGen outputs in $\Open(\osk,\ipk,\sig,
  0,\msg,\feval^0)$. Internally, the call to \Open runs $\finsp^{\upk}$.
\item[$1/0 \gets \Judge(\gpk,\pi,\upk,\sig,\msg)$.] Parses \gpk as $(\ipk,
  \opk)$, and returns whatever \CUASGen outputs in $\Judge(\opk,\upk,\pi,\sig,
  0,\msg)$.
\end{description}

@@

\subsubsection{\CUASRing Construction.} %
Building a ring signature scheme according to the model in \figref{fig:model-rs}
is essentially a $(\fissue^{\sring},\feval^{\sring,\dattrs},\finsp^0)$-restriction
of our $\CUASGen^{hide-iss}$ construction. The construction is as follows:

@@

\begin{description}
%\item[$\parm \gets \Setup(\secpar,\AttrSpace)$.] As in $\CUASGen^{hide-iss}$.
\item[$((\pk_1,\sk_1),...,(\pk_n,\sk_n)) \gets KeyGen(\secpar)$.] Runs
  $\parm \gets \Setup(\secpar)$ from $\CUASGen^{hide-iss}$, as well as $n$
  instances of $(\ipk_i,\isk_i) \gets \IKeyGen(\parm,\fissue^{\sring})$, where
  $\sring = \lbrace \ipk_i \rbrace_{i\in[n]}$, and $(\opk,\osk) \gets
  \OKeyGen(\parm,\finsp^0)$. 
\item[$\langle \cred,\bot,\utrans,\bot \rangle \gets
  \langle \Obtain(\usk,\scred,\attrs),\Issue(\isk,\sipk=\attrs,\attrs)\rangle.$]
  A user, with $\usk=\isk_i$ and $\upk=\ipk_i$ for some $i \in [n]$, acts both
  as user and issuer to self-issue a credential for an attribute set \attrs such
  that $\attrs \subseteq \sring$, where \sring is the set of public keys used to
  define $\fissue^{\sring}$.
\item[$(\sig,\yeval) \gets \Sign(\usk,\opk,\cred,\msg,\feval).$] As in
  $\CUASGen^{hide-iss}$, using $\feval^{\sring,\dattrs}$ as evaluation
  function, using as signing credential the self-issued credential. Note that
  $\dattrs \subseteq \attrs = \sring$ defines the subring to use for the
  produced signature.
\item[$1/0 \gets \Verify(\opk,\sipk,\sig,\yeval,\msg,\feval).$] As in
  $\CUASGen^{hide-iss}$, making $\sipk=\yeval=\lbrace \ipk_i
  \rbrace_{i\in\dattrs}$.
\end{description}

>>>>

  \scalebox{0.9}{
    \begin{minipage}[t]{\textwidth}
      \textbf{Issuance functions:}
      \begin{align}
        & \fissue^1(\cdot,\cdot,\cdot) \coloneqq 1 \nonumber \\
        & \fissue^{single,F,I,L}(\upk,\cdot,\cdot) \coloneqq
          \pcif F(I||\upk) \in L~\pcreturn 0;~\pcelse \pcreturn F(I||\upk)
          \nonumber \\
        & \fissue^{\sring}(\upk,\attrs,\cdot) \coloneqq
          \pcreturn (\attrs = \sring \land \upk \in \attrs) \nonumber \\
        & \fissue^{l,\dattrs}(\cdot,\attrs,(\cid,\cattrs)) \coloneqq
          \pcreturn (\attrs_1 = l+1 \land \attrs \subseteq
          \cup_{i\in\dattrs} \cattrs_i) \nonumber
      \end{align}

@@

\subsubsection{\CUASGS construction.} %
We show that the $(\fissue^{single,L},\feval^0,\finsp^{\upk})$-\CUASGen
restriction, is a secure group signature scheme according to \cite{bsz05}.
Observe that the $\fissue^{single,F,I,L}$ function is further parameterized with
a list $L$ maintained by the issuer and must be fetched by users prior to
joining. It restricts that any user can have at most one credential (associated
to a same user key pair). We first quickly define the algorithms, and then
prove security.

\begin{description}
\item[$(\gpk,\isk,\osk) \gets KeyGen(1^\secpar)$.] Runs the \Setup algorithm
  of \CUASGen, and one instance of \KeyGen and \ISet with
  $\fissue^{single,F,I,L}$ (both for the same user, who will be the only issuer
  in the GS scheme) and \OKeyGen. Assigns the public keys to \gpk.
\item[$(\upk,\usk) \gets \UKeyGen(1^\secpar)$.] Runs \KeyGen from \CUASGen.
\item[$\langle \cred,\utrans \rangle \gets
  \langle\Obtain(\usk,\ipk),\Issue(\isk,\upk)\rangle$.] Runs $\langle\Obtain,
  \Issue\rangle$ as in \CUASGen, with $\attrs \gets \emptyset$.
\item[$\sig \gets \Sign(\gpk,\cred,\msg)$.] Parses \gpk as $(\ipk,\opk)$, and
  runs $(\sig,0) \gets \Sign(\usk,\opk,\cred,\msg,\feval^0)$ from \CUASGen,
  where $\yeval = 0$ is the constant output of $\feval^0$.
\item[$1/0 \gets \Verify(\gpk,\sig,\msg)$.] Parses \gpk as $(\ipk,\opk)$, and
  returns whatever $\Verify(\opk,\ipk,\sig,0,\msg,\feval^0)$ from \CUASGen
  outputs.
\item[$(\upk,\pi) \gets \Open(\gpk,\osk,\trans,\sig,\msg)$.] Parses \gpk as
  $(\ipk,\opk)$, and returns whatever \CUASGen outputs in $\Open(\osk,\ipk,\sig,
  0,\msg,\feval^0)$. Internally, the call to \Open runs $\finsp^{\upk}$.
\item[$1/0 \gets \Judge(\gpk,\pi,\upk,\sig,\msg)$.] Parses \gpk as $(\ipk,
  \opk)$, and returns whatever \CUASGen outputs in $\Judge(\opk,\upk,\pi,\sig,
  0,\msg)$.
\end{description}

@@

\subsubsection{\CUASRing Construction.} %
Building a ring signature scheme according to the model in \figref{fig:model-rs}
is essentially a $(\fissue^{\sring},\feval^{\sring,\dattrs},\finsp^0)$-restriction
of our $\CUASGen^{hide-iss}$ construction. In a nutshell, we let users self-issue
credentials where the attributes are (a subset of encodings of) the public keys
of the users in the system -- including their own public key. Then, a ring
signature is just a $\CUASGen^{hide-iss}$ signature that reveals a subset of
the attributes -- i.e., a subset of the keys of the users in the system. In more
detail, the construction is as follows:

@@

\begin{description}
%\item[$\parm \gets \Setup(\secpar,\AttrSpace)$.] As in $\CUASGen^{hide-iss}$.
\item[$((\pk_1,\sk_1),...,(\pk_n,\sk_n)) \gets KeyGen(\secpar)$.] Runs
  $\parm \gets \Setup(\secpar)$ from $\CUASGen^{hide-iss}$. Then, for each of
  the $i \in [n]$ users to generate, run $(\upk_i,\usk_i) \gets \KeyGen(\parm)$,
  and $\ipk_i \gets \ISet((\upk_i,\usk_i),\fissue^{\sring})$, where $\sring =
  \lbrace \upk_i \rbrace_{i\in[n]}$. Run also $(\opk,\osk) \gets \OKeyGen(\parm,
  \finsp^0)$. Set $\pk_i \gets (\ipk_i,\opk)$ and $\sk_i \gets \usk_i$, for
  $i\in[n]$.
\item[$\Sig \gets \Sign(\sk_i,R,\msg).$]
  The signing user, with $\sk_i=\usk$ and $\pk_i=(\ipk_i,\opk)$ for some $i \in
  [n]$, where $\pk_i \in R$, first acts both as user and issuer to self-issue a
  credential \Cred over an attribute set \attrs such that $\attrs \subseteq
  \sring$. The user picks some \dattrs such that $\dattrs \subseteq [|\attrs|]$,
  and computes the ring signature by running $\Sig = (\sig,\yeval) \gets
  \Sign(\usk,\opk,\Cred,\msg,\feval^{\sring,\dattrs})$ from
  $\CUASGen^{hide-iss}$. Note that \dattrs defines the public keys within
  $\attrs \subseteq \sring$ to be revealed through \yeval.
\item[$1/0 \gets Verify(R,\Sig,\msg)$.] Parses \Sig as $(\sig,\yeval)$ and
  runs $\Verify(\opk,\yeval=\lbrace \ipk_i\rbrace_{i\in\dattrs},\sig,\yeval,
  \msg,\feval^{\sring,\dattrs})$ as in $\CUASGen^{hide-iss}$.
\end{description}
